Exploring Homicide Trends in Toronto: A Seventeen-Year Statistical Overview (2004-2020)

### 2024-01-22 outputs/paper/paper.qmd
Update paper.qmd, aesthetic changes

# Summarize and arrange the data
homicide_types_per_year <- data |>
  group_by(occurrence_year, homicide_type) |>
  summarise(Count = n(), .groups = 'drop') |>
  arrange(occurrence_year, homicide_type)
homicide_types_per_year

# Plot the data
ggplot(homicide_types_per_year, aes(x = occurrence_year, y = Count, color = homicide_type)) +
  geom_point() +
  theme_minimal() + # Make the theme neater
  labs(x = "Occurrence Year", y = "Number of Homicides", color = "Homicide Type")

>>>>

homicide_types_per_year <- data |>
  group_by(occurrence_year, homicide_type) |>
  summarise(Count = n(), .groups = 'drop') |>
  arrange(occurrence_year, homicide_type)
homicide_types_per_year

ggplot(homicide_types_per_year, aes(x = occurrence_year, y = Count, color = homicide_type)) +
  geom_point() +
  theme_minimal() + # Make the theme neater
  labs(x = "Occurrence Year", y = "Number of Homicides", color = "Homicide Type")
